Article title

### 2017-08-03 paper-webserver.tex
ADD: some words that look like a 3rd para

% 4. benefits: rapid analyses in real-time -> huge comparisons, replace reference labs -> time & money saved, future work -> expand analyses, more genomes, more species
This allows large-scale analyses, such as epidemiological associations between specific genotypes, biomarkers, host, source, and other metadata, and statistical significance testing of genome markers for user-defined groups.

>>>>

% 4. benefits: rapid analyses in real-time -> huge comparisons, replace reference labs -> time & money saved, future work -> expand analyses, more genomes, more species
Integrating task distribution with graph storage allows large-scale analyses, such as epidemiological associations between specific genotypes, biomarkers, host, source, and other metadata, and statistical significance testing of genome markers for user-defined groups.
By supporting multiple \textit{in-silico} subtyping options, the platform can function as an online reference laboratory.
Currently, the platform has been tested with XXX genome files and result storage for XX analyses modules.
Future work will focus on expanding available analyses and supporting different species, which can be connected to the existing graph database without need for recalculation.
To complement existing platforms such as IRIDA, analyses modules are individually packaged and easily integrated into Galaxy \cite{goecks2010galaxy} based platforms.
The website and source-code are available at \url{https://superphy.github.io/}. \par
